Efficient pedigree recording for fast population genetics simulation

### 2018-01-09 peq_abstract.tex
revise last sentence as per Jaime's suggestion

We present a new approach to recording the entire history of a population during forward-time, individual-based
population genetics simulation.  Our approach uses extensions of the data structures in the \emph{msprime} software to
record the marginal genealogies of all individuals (including ancient samples when needed), eliminating the need to
expicitly simulate mutations not affecting fitness.  We show that recording histories substantially reduces the run-time
complexity of two different forward simulation engines, providing run time improvements of at least an order of
magnitude and the possibility of substantial reductions in memory requirements.  We will also describe more general
features of the new \emph{msprime} API that apply both to simulation methods and more generally to storage of
population-genomic information.

>>>>

We present a new approach to recording the entire history of a population during forward-time, individual-based
population genetics simulation.  Our approach uses extensions of the data structures in the \emph{msprime} software to
record the marginal genealogies of all individuals (including ancient samples when needed), eliminating the need to
expicitly simulate mutations not affecting fitness.  We show that recording histories substantially reduces the run-time
complexity of two different forward simulation engines, providing run time improvements of at least an order of
magnitude and the possibility of substantial reductions in memory requirements.  We will also describe the API, new in
\emph{msprime} 0.5.0, that enables our simulation method.  These new features generally enable storage of
population-genomic information within the \emph{msprime} data structures from third-party code.
